---
title: "cB58 Distributed Spectral Search"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This report summarizes the retained Top-100 candidates from a distributed spectral-matching search for spectra resembling the cB58 Lyman-break galaxy reference.

The search itself is implemented in `project.R` and distributed with HTCondor using `project.sub`. Each job processes an independent archive of FITS spectra and writes a ranked result CSV. `merge.sh` combines those partial outputs into the global Top 100.

## Load candidate results

```{r}
candidates <- read.csv("best100.csv")
candidates <- candidates[order(candidates$distance), ]
head(candidates, 10)
```

## Best candidate

```{r}
best <- candidates[1, ]
best
```

## Top-20 distance profile

```{r}
top <- head(candidates, 20)
barplot(
  top$distance,
  names.arg = top$spectrumID,
  las = 2,
  cex.names = 0.55,
  ylab = "Euclidean spectral distance",
  main = "Top 20 cB58 spectral matches"
)
```

## Candidate distribution

```{r}
hist(
  candidates$distance,
  breaks = 20,
  xlab = "Euclidean spectral distance",
  main = "Distance distribution among Top-100 candidates"
)
```

## Interpretation

Lower distance indicates a closer sliding-window match to the cB58 reference flux sequence. The retained table is therefore a ranked candidate list for follow-up inspection rather than a final astrophysical classification by itself.
