---
title: "hw4"
author: "danielye,ye97@wisc.edu"
date: "2022/12/6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Summary

## First write bascic sub scripts. 
We first should  write a basic and simple script, such as R language, python, etc.Make sure our scripts can run on the case data.

For examples.

```{r eval=FALSE, include=TRUE}
install.packages("FITSio", repos="https://cran.r-project.org")
install.packages("tidyverse", repos="https://cran.r-project.org")
require("FITSio")
require("tidyverse")
args = commandArgs(trailingOnly=TRUE)

cb5file='cB58_Lyman_break.fit'
otherfile=args[1]



cB58 = readFrameFromFITS("cB58_Lyman_break.fit")
n_cB58 = length(cB58)
files = list.files(otherfile)
n.files = length(files)

distance = function(A, B) {
  return(sqrt(sum((A - B)^2)))
}

res = data.frame(min_d=c(),file=c(),best_j=c())
library(tidyverse)
for (i in 1:n.files) {
  path = paste(sep="", otherfile, files[i])
  # cat(sep="", "path=", path, "\n")
  noisy = readFrameFromFITS(path)
  
  n_noisy = length(noisy$flux)
  
  # cat(sep="", "n_cB58=", n_cB58, ", n_noisy=", n_noisy, "\n")
  
  min_d = 1000000
  best_j = 10
  for (j in 1:(n_noisy - n_cB58)) {
    slice = noisy$flux[j:(j + n_cB58)]
    ##print(str(slice))
    d = distance(cB58$FLUX, slice)
    if (is.na(d)) {
      # cat(sep="", "NA at j=", j, "\n")
    }
    if (d < min_d) {
      min_d = d
      best_j = j
    }
    # cat(sep="", "j=", j, ", d=", d, ", best_j=", best_j, ", min_d=", min_d, "\n")
  }
  cat(sep=",",min_d,files[i],best_j,"\n")
  res <- res %>% add_row(min_d=min_d,file=files[i],best_j=best_j)
}

write.csv(res,"./hw4.csv",row.names=FALSE)

```



## Pass parameters using shell script
After we have written the core script, use the parameters as the entry point for the calculation.

Write parameters into the shell script to be passed into the core script code script for easy modification and adjustment at any time.

for examples.

```{r eval=FALSE, include=TRUE}
#!/bin/bash

# untar your R installation
tar -xzf R402.tar.gz
tar -xzf 3586.tgz 3586

# make sure the script will use your R installation, 
# and the working directory as its home location
export PATH=$PWD/R/bin:$PATH
export RHOME=$PWD/R
export R_LIBS=$PWD/packages

# run your script
Rscript q3_1.R './3586/'

```



## Then use CHTC

Finally, we use CHTC to schedule our shell scripts to ensure that the power of the cluster can be used


```{r eval=FALSE, include=TRUE}
universe = vanilla
log    =    log/q3_1-chtc_$(Cluster)_$(Process).log
error  =  error/q3_1-chtc_$(Cluster)_$(Process).err
output = output/q3_1-chtc_$(Cluster)_$(Process).out


executable = ./q3_1.sh


should_transfer_files = YES
when_to_transfer_output = ON_EXIT
transfer_input_files = http://proxy.chtc.wisc.edu/SQUID/chtc/R402.tar.gz,q3_1.R, /home/groups/STAT605/boss/cB58_Lyman_break.fit,/home/groups/STAT605/boss/tgz/3586.tgz

request_cpus = 2
request_memory = 2GB
request_disk = 300MB

queue 3
```







# Result

## read the hw4best.csv

```{r}
df = read.csv("hw4best100.csv",header = T)
head(df)
```



## Plot 

```{r eval=TRUE, include=TRUE}
for (x in 0:9){
  low = x*10 + 1
  high = x*10 + 10
  temp = df[c(low:high),][,c('distance','spectrumID')]
  barplot(temp$distance,names.arg = temp$spectrumID)
}

```



# my problem
While I was writing my homework, I encountered some problems as described below

- I'm new to the shell and new to passing arguments. Spent a lot of time on this block.

- I can use CHTC software and scripts normally, but I don't know how to use its parallel function to guarantee one data one node. More references and examples in class might be helpful.















